Actuator line modeling of vertical-axis turbines

### 2016-05-02 paper.tex
Add address for Goude

\author{P.~Bachant, A.~Goude, and M.~Wosnik}

\address{Center for Ocean Renewable Energy, University of New Hampshire, 24
Colovos Rd., Durham, NH, 03824, USA}

>>>>

\author{P.~Bachant\textsuperscript{1}, A.~Goude\textsuperscript{2}, and
M.~Wosnik\textsuperscript{1}}

\address{\textsuperscript{1}Center for Ocean Renewable Energy,
University of New Hampshire, 24
Colovos Rd., Durham, NH, 03824, USA \\
\textsuperscript{2}Department of Engineering Sciences,
Division of Electricity, Uppsala University, Uppsala 751 21, Sweden}
